Copy number inference with InferCNV

### 2024-11-19 analyses/cell-type-ewings/template_notebooks/cnv-workflow/04-infercnv.Rmd
account for weird chromosomes showing up

# remove MT and GL chr, comments in docs recommend that these are not useful and can be inaccurate
chr_columns_to_keep <- which(!stringr::str_detect(names(coldata_df), "chrMT|chrGL"))
all_cnv_df <- coldata_df[, chr_columns_to_keep]
```

>>>>

# remove MT and GL chr, comments in docs recommend that these are not useful and can be inaccurate
# only keep coldata columns and chr1-22 columns
chr_columns <- paste0("chr", seq(1,22), collapse = "|")
all_colnames_keep <- paste0(c(names(colData(sce)), "UMAP1", "UMAP2|"), collapse = "|") |> 
  paste0(chr_columns, collapse = "|")
chr_columns_to_keep <- which(stringr::str_detect(names(coldata_df), all_colnames_keep))
all_cnv_df <- coldata_df[, chr_columns_to_keep]
```
